\documentclass[DM,lsstdraft,authoryear,toc]{lsstdoc}
% lsstdoc documentation: https://lsst-texmf.lsst.io/lsstdoc.html
\input{meta}

% Package imports go here.
%\usepackage{graphicx}
%\usepackage{url}
%\usepackage{latexsym}
%\usepackage{color}
%\usepackage{enumitem}

% Local commands go here.

%If you want glossaries
%\input{aglossary.tex}
%\makeglossaries

\title{Community Science Use Cases}

% Optional subtitle
% \setDocSubtitle{A subtitle}

\author{%
Melissa Graham, Andrés A. Plazas Malagón, Jeff Carlin, Leanne Guy, Christina Adair, Greg Madejski
}

\setDocRef{RTN-002}
\setDocUpstreamLocation{\url{https://github.com/rubin-observatory/rtn-002}}

\date{\vcsDate}

% Optional: name of the document's curator
% \setDocCurator{The Curator of this Document}

\setDocAbstract{%
User profiles and analysis and support use cases (workflows) for Rubin community science.
}

% Change history defined here.
% Order: oldest first.
% Fields: VERSION, DATE, DESCRIPTION, OWNER NAME.
% See LPM-51 for version number policy.
\setDocChangeRecord{%
  \addtohist{1}{2021-03-05}{Released.}{Melissa Graham}
  \addtohist{2}{2023-04-19}{Add user profiles.}{Andrés A. Plazas Malagón}
  \addtohist{3}{2024-12-01}{Reorganize document (SP-1758).}{Melissa Graham}
}

\begin{document}

% Create the title page.
\maketitle
% Frequently for a technote we do not want a title page  uncomment this to remove the title page and changelog.
% use \mkshorttitle to remove the extra pages

% ADD CONTENT HERE
% You can also use the \input command to include several content files.

\section{Introduction}

The contents of this document are under development and are subject to change.

The Community Science Team (CST) in the Rubin System Performance department maintains this set of user profiles and use cases
to capture the range of anticipated needs regarding scientific analyses with the Rubin software and data products.

This document guides the development of a process to scientifically validate user-facing resources for scientific analysis,
such as the Rubin Science Platform (RSP), documentation, tutorials, and activities.
To ``scientifically validate" the RSP means to confirm that the RSP's functionality meets the scientific needs
of its users, and that users are able to do their science with the RSP's tools.
This document also guides the development of Rubin's Model for Community Science \citedsp{RTN-004}.

\textbf{User profiles} are designed to represent the diverse user community of the RSP:
different experience and expertise backgrounds, scientific motivations, and accessibility needs.

\textbf{Analysis use cases} are designed to represent the variety of types of analysis that
users will do with the RSP, such as subsetting, visualization, model fitting, and reprocessing.
These use cases help to define the limitations of the RSP as well, and identify analysis
that requires external resources (independent data access centers; IDACs).

\textbf{Support use cases} are designed to provide workflow examples of Rubin's issue resolution
process, to illuminate how users report problems and get support, and how staff from across
Rubin participate in user support.
These use cases include, e.g., trouble with scientific analysis,
instrumentation faults, software bugs.

\clearpage
\section{User Profiles}

\input{user_profiles.tex}


\clearpage
\section{Analysis Use Cases}

These analysis use cases represent general things that users want to do in the Rubin Science Platform,
using specific scientific examples.
They are not 1:1 related to the user profiles above, although some of the more advanced analysis
use cases, for example, would be much more likely to be done by a heavy user.

The analysis use cases progress from ``simple" to ``more complicated".
These will serve as the basis for usability tests and the CST's process for science validation of
the RSP.

\subsection{Rubin Science Platform}

\input{analysis_rsp.tex}

\subsection{Independent Data Access Centers (IDACs)}




\clearpage
\section{Support Use Cases}

\clearpage
\input{uc000.tex}

\clearpage
\input{uc001.tex}

\clearpage
\input{uc002.tex}

\clearpage
\subsection{A Camera Fault Requires Modification of the Alert Production System}
\input{uc003.tex}

\clearpage
\subsection{Large Queries: Community Self-Help Using CST Resources}
\input{uc004.tex}

\clearpage
\subsection{Science Platform Bug: A Help Desk Submission}
\input{uc005.tex}

\clearpage
\subsection{Survey Strategy Alteration for Photometric Redshifts}
\input{uc006.tex}

\clearpage
\subsection{A Science-Driven Modification to a Data Product}
\input{uc007.tex}



\appendix
% Include all the relevant bib files.
% https://lsst-texmf.lsst.io/lsstdoc.html#bibliographies
\section{References} \label{sec:bib}
\renewcommand{\refname}{} % Suppress default Bibliography section
\bibliography{local,lsst,lsst-dm,refs_ads,refs,books}

% Make sure lsst-texmf/bin/generateAcronyms.py is in your path
\section{Acronyms} \label{sec:acronyms}
\input{acronyms.tex}
% If you want glossary uncomment below -- comment out the two lines above
% \printglossaries





\end{document}
