\subsection{S-005: Science Platform Issue - A Help Desk Submission}

\textbf{Issue origin and description} \\
A user submits a Help Desk ticket regarding an issue they encountered in the Rubin Science Platform (RSP).
The CST is responsible for determining whether the issue is a user error or an actual bug and taking appropriate steps to resolve it.

\textbf{Success scenario(s)} \\
The ticket is resolved by either: (1) solving a user issue that is not actually a bug, or (2) identifying the bug and providing detailed information to the RSP development team.
While the ultimate goal is fixing the bug, providing a short-term workaround for the user is a critical success factor for the CST.

\textbf{Success workflow} \\
Step 1. CST confirms that the reported bug is reproducible. \\
Step 2. CST communicates the details of the bug to the RSP development team. \\
Step 3. CST provides a short-term workaround to the user, if possible. \\
Step 4. RSP developers investigate and fix the bug. \\
Step 5. A new version of the RSP, incorporating the fix, is rolled out. \\

\textbf{Alternative success scenario} \\
The CST determines that the issue is not a bug but rather a misunderstanding or error by the user.
In this case, the CST provides clarification or instructions to help the user resolve their issue.

\textbf{Failure scenario(s)} \\
The bug cannot be reproduced, and no workaround is available. \\
The issue persists without a resolution, potentially affecting the robustness of the RSP.\\

\textbf{Risks} \\
Users may lose confidence in the RSP if bugs are not addressed promptly or if no workarounds are provided. \\
The lack of timely fixes may lead to broader disruptions in the community's ability to use the platform effectively. \\
Recurrent or unresolved bugs may increase the CST and RSP development teams' workload.\\

\textbf{Related information (optional)} \\
\textbf{Priority:} Most cases are likely to be low priority. \\
\textbf{Performance Target:} Resolution within days to weeks, depending on the issue complexity. \\
\textbf{Frequency:} Infrequent \\

\textbf{Preconditions for success} \\
The RSP is operational and actively used by the community. \\
A functional ticketing system is in place to track and manage Help Desk submissions. \\
Communication channels between the CST and RSP development teams (e.g., JIRA, Slack) are active and effective. \\
